---
title: "03_pres_analysis"
author: "Sglatt"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")} 
if (!require("tidyverse")) {install.packages("tidyverse"); require("tidyverse")} 
```

# path to pull individual central symptom files from
```{r set up}
path = "Paper_res/Imputed_results"
```

# read in each network central mean and variable symptoms 
```{r Data}
#### means ####
files_to_read = list.files(
  path = path,       
  pattern = "_centr_means_imputed\\.csv$", 
  recursive = TRUE,         
  full.names = TRUE          
)

data_lst_means = lapply(files_to_read, read.csv) 
combined_data_means <- do.call(rbind, data_lst_means)
names(data_lst_means) <- basename(files_to_read) 
unique(combined_data_means$measure)

#### variability ####
files_to_read = list.files(
  path = path,       
  pattern = "_centr_sd_imputed\\.csv$", 
  recursive = TRUE,          
  full.names = TRUE         
)

data_lst_sds = lapply(files_to_read, read.csv)  
combined_data_sds <- do.call(rbind, data_lst_sds)
names(data_lst_sds) <- basename(files_to_read) 
```

# how many symptoms appeared in means networks?
```{r}
strength_counts_means <- table(combined_data_means$node[combined_data_means$measure == "Strength"])
(strength_df_means <- as.data.frame(strength_counts_means))
```

# how many symptoms appeared in variability networks?
```{r}
strength_counts_sds <- table(combined_data_sds$node[combined_data_sds$measure == "Strength"])
(strength_df_sds <- as.data.frame(strength_counts_sds))
```

# how many symptoms appeared in means and variability networks across participants?
```{r}
(intersect(strength_df_means$Var1, strength_df_sds$Var1))
```

# how many symptom ~pairs appeared in means networks across participants?
```{r Means frequent combination nodes}
co_occurrence_list <- list()

for (participant_id in names(data_lst_means)) {
  df <- data_lst_means[[participant_id]]
  strength_data <- df %>% filter(measure == "Strength")
  nodes <- strength_data$node

  if (length(nodes) > 1) {
    node_pairs <- combn(nodes, 2)
    
    # Sort pairs to avoid duplicates 
    sorted_pairs <- apply(node_pairs, 2, function(x) paste(sort(x), collapse = "__"))
    
    # ADD PARTICIPANT ID!!
    participant_pairs <- data.frame(Node_Pair = sorted_pairs, 
                                    Participant_ID = gsub("_centr_means_imputed.csv", "", participant_id))  
    
    co_occurrence_list[[participant_id]] <- participant_pairs
  }
}

# frequency of each symptom pair in mean networks
co_occurrence_combined <- do.call(rbind, co_occurrence_list)

co_occurrence_counts <- co_occurrence_combined %>%
  group_by(Node_Pair) %>%
  summarize(Frequency = n(), Participants = paste(unique(Participant_ID), collapse = ", ")) %>%
  arrange(desc(Frequency))

colnames(co_occurrence_counts) <- c("Node_Pair", "Frequency", "Participants")

(co_occurrence_counts_means <- co_occurrence_counts[order(-co_occurrence_counts$Frequency), ])

(Mean_pairs <- ggplot(co_occurrence_counts_means, aes(x = reorder(Node_Pair, Frequency), y = Frequency)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +  
  labs(title = "Frequency of Unique Co-occurring Symptom Pairs - mean",
       x = "Symptom Pairs",
       y = "Frequency") +
  theme_minimal())
```

# Symptom pairs with one specified central means symptom 
```{r}
central_symptom <- "feelfat"

co_occurrence_counts_means$Node_Pair <- as.character(co_occurrence_counts_means$Node_Pair)

(central_pairs <- co_occurrence_counts_means %>%
  filter(grepl(central_symptom, Node_Pair))) # filter for pairs with specified symptom above

paired_symptoms <- do.call(rbind, strsplit(central_pairs$Node_Pair, "__")) # Split for itemized
(paired_symptoms <- unique(paired_symptoms[paired_symptoms != central_symptom])) # list of all it co-occurred with
```

# how many symptom ~pairs appeared in variability networks across participants?
```{r SD frequent combination nodes}
co_occurrence_list <- list()

for (participant_id in names(data_lst_sds)) {
  df <- data_lst_sds[[participant_id]]
  strength_data <- df %>% filter(measure == "Strength")
  nodes <- strength_data$node

  if (length(nodes) > 1) {
    node_pairs <- combn(nodes, 2)
    
    # Sort pairs to avoid duplicates 
    sorted_pairs <- apply(node_pairs, 2, function(x) paste(sort(x), collapse = "__"))
    
    # ADD PARTICIPANT ID!!
    participant_pairs <- data.frame(Node_Pair = sorted_pairs, 
                                    Participant_ID = gsub("_centr_sd_imputed.csv", "", participant_id))  
    
    co_occurrence_list[[participant_id]] <- participant_pairs
  }
}

# frequency of each symptom pair in fluctuating networks
co_occurrence_combined <- do.call(rbind, co_occurrence_list)

co_occurrence_counts <- co_occurrence_combined %>%
  group_by(Node_Pair) %>%
  summarize(Frequency = n(), Participants = paste(unique(Participant_ID), collapse = ", ")) %>%
  arrange(desc(Frequency))

colnames(co_occurrence_counts) <- c("Node_Pair", "Frequency", "Participants")

(co_occurrence_counts_SD <- co_occurrence_counts[order(-co_occurrence_counts$Frequency), ])

(SD_pairs <- ggplot(co_occurrence_counts_SD, aes(x = reorder(Node_Pair, Frequency), y = Frequency)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +  
  labs(title = "Frequency of Unique Co-occurring Symptom Pairs - SD",
       x = "Symptom Pairs",
       y = "Frequency") +
  theme_minimal())
```

# Symptom pairs with one specified central variable symptom 
```{r}
central_symptom <- "feelfat"

co_occurrence_counts_SD$Node_Pair <- as.character(co_occurrence_counts_SD$Node_Pair)

(central_pairs <- co_occurrence_counts_SD %>%
  filter(grepl(central_symptom, Node_Pair))) # filter for pairs with specified symptom above

paired_symptoms <- do.call(rbind, strsplit(central_pairs$Node_Pair, "__")) # Split for itemized
(paired_symptoms <- unique(paired_symptoms[paired_symptoms != central_symptom])) # list of all it co-occurred with
```

# how many unique symptom sets across means networks?
```{r Means node combinations}
all_combos <- list()
for (df in data_lst_means) {
  df_means <- df %>% filter(measure == "Strength")  
  split_data <- split(df_means, list(df_means$graph, df_means$type))
  for (subset in split_data) {
    if (nrow(subset) > 0) {
      nodes_sorted <- paste(sort(subset$node), collapse = " ")
      all_combos <- c(all_combos, nodes_sorted)
    }
  }
}

combo_counts <- data.frame(table(unlist(all_combos)))
colnames(combo_counts) <- c("Node Combination", "Count")
combo_counts # all unique
```

# how many unique symptom sets across variability networks?
```{r SD node combinations}
all_combos <- list()
for (df in data_lst_sds) {
  df_means <- df %>% filter(measure == "Strength")  
  split_data <- split(df_means, list(df_means$graph, df_means$type))
  for (subset in split_data) {
    if (nrow(subset) > 0) {
      nodes_sorted <- paste(sort(subset$node), collapse = " ")
      all_combos <- c(all_combos, nodes_sorted)
    }
  }
}

combo_counts <- data.frame(table(unlist(all_combos)))
colnames(combo_counts) <- c("Node Combination", "Count")
combo_counts # all unique
```

