---
title: "05_symptoms_pairs"
author: "Sglatt"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
if (!require("dplyr")) {
  install.packages("dplyr")
  require("dplyr")
}
if (!require("ggplot2")) {
  install.packages("ggplot2")
  require("ggplot2")
}
if (!require("tidyverse")) {
  install.packages("tidyverse")
  require("tidyverse")
}
```

# path to pull individual central symptom files from
```{r set up}
path <- "Paper_res/Imputed_results"
```

# read in each network central mean and variable symptoms 
```{r Data}
#### means ####
files_to_read <- list.files(
  path = path,
  pattern = "_centr_means_imputed\\.csv$",
  recursive = TRUE,
  full.names = TRUE
)

data_lst_means <- lapply(files_to_read, read.csv)
combined_data_means <- do.call(rbind, data_lst_means)
names(data_lst_means) <- basename(files_to_read)
unique(combined_data_means$measure)

#### variability ####
files_to_read <- list.files(
  path = path,
  pattern = "_centr_sd_imputed\\.csv$",
  recursive = TRUE,
  full.names = TRUE
)

data_lst_sds <- lapply(files_to_read, read.csv)
combined_data_sds <- do.call(rbind, data_lst_sds)
names(data_lst_sds) <- basename(files_to_read)
```

# how many symptoms appeared in means networks?
```{r Mean freq}
strength_counts_means <- table(combined_data_means$node[combined_data_means$measure == "Strength"])
(strength_df_means <- as.data.frame(strength_counts_means))
strength_df_means$label <- paste(strength_df_means$Var1, "\n", strength_df_means$Freq)
```

# how many symptoms appeared in variability networks?
```{r SD freq}
strength_counts_sds <- table(combined_data_sds$node[combined_data_sds$measure == "Strength"])
(strength_df_sds <- as.data.frame(strength_counts_sds))
strength_df_sds$label <- paste(strength_df_sds$Var1, "\n", strength_df_sds$Freq)
```

# treemaps & sunbursts of frequency of symptoms in means and variability networks
```{r SD freq}
# mean network
# pdf("05_Output/Treemap_means.pdf", width = 12, height = 8)
(treemap(
  strength_df_means,
  index = "label",
  vSize = "Freq",
  vColor = "Freq",
  draw.labels = TRUE,
  type = "value",
  title = "Frequency of Nodes in Mean Networks",
  palette = "Blues",
  fontsize.labels = 14,
  fontcolor.labels = "white",
  force.print.labels = TRUE
))
# dev.off()

# variability network
# pdf("05_Output/Treemap_SDs.pdf", width = 12, height = 8)
(treemap(
  strength_df_sds,
  index = "label",
  vSize = "Freq",
  vColor = "Freq",
  draw.labels = TRUE,
  type = "value",
  title = "Frequency of Nodes in Variability Networks",
  palette = "Purples",
  fontsize.labels = 14,
  fontcolor.labels = "white",
  force.print.labels = TRUE
))
# dev.off()

# Subursts; Download as png on top of the images
plot_ly(
  labels = strength_df_means$label,
  parents = "",
  values = strength_df_means$Freq,
  type = "sunburst"
)

plot_ly(
  labels = strength_df_sds$label,
  parents = "",
  values = strength_df_sds$Freq,
  type = "sunburst"
)
```

# how many symptoms appeared in means and variability networks across participants?
```{r Common}
(intersect(strength_df_means$Var1, strength_df_sds$Var1))
```

# how many symptoms appeared in uiquely in means or  variability networks across participants?
```{r unique}
(setdiff(strength_df_means$Var1, strength_df_sds$Var1)) # Means not SDs
(setdiff(strength_df_sds$Var1, strength_df_means$Var1)) # SDs not means
```

# how many unique symptom sets across means networks?
```{r Means node sets}
all_combos <- list()
for (df in data_lst_means) {
  df_means <- df %>% filter(measure == "Strength")
  split_data <- split(df_means, list(df_means$graph, df_means$type))
  for (subset in split_data) {
    if (nrow(subset) > 0) {
      nodes_sorted <- paste(sort(subset$node), collapse = " ")
      all_combos <- c(all_combos, nodes_sorted)
    }
  }
}

combo_counts <- data.frame(table(unlist(all_combos)))
colnames(combo_counts) <- c("Node Combination", "Count")
combo_counts

# WITH IDs!!!
all_combos <- list()
for (participant_id in names(data_lst_sds)) {
  df <- data_lst_sds[[participant_id]]
  participant_id <- gsub("_centr_means_imputed.csv", "", participant_id) # Clean ID

  df_means <- df %>% filter(measure == "Strength")
  split_data <- split(df_means, list(df_means$graph, df_means$type))

  for (subset in split_data) {
    if (nrow(subset) > 0) {
      nodes_sorted <- paste(sort(subset$node), collapse = " ")
      combo_entry <- data.frame(
        `Node Combination` = nodes_sorted,
        `Participant_ID` = participant_id
      )
      all_combos <- append(all_combos, list(combo_entry))
    }
  }
}

combo_counts <- do.call(rbind, all_combos)

combo_summary <- combo_counts %>%
  group_by(`Node.Combination`) %>%
  summarise(Count = n(), Participants = toString(unique(`Participant_ID`)))

combo_summary
```

# how many unique symptom sets across variability networks?
```{r SD node sets}
all_combos <- list()
for (df in data_lst_sds) {
  df_means <- df %>% filter(measure == "Strength")
  split_data <- split(df_means, list(df_means$graph, df_means$type))
  for (subset in split_data) {
    if (nrow(subset) > 0) {
      nodes_sorted <- paste(sort(subset$node), collapse = " ")
      all_combos <- c(all_combos, nodes_sorted)
    }
  }
}


combo_counts <- data.frame(table(unlist(all_combos)))
colnames(combo_counts) <- c("Node Combination", "Count")
combo_counts
```

```{r}
```

# how many symptom ~pairs appeared in means networks across participants?
```{r Means combination nodes}
co_occurrence_list <- list()

for (participant_id in names(data_lst_means)) {
  df <- data_lst_means[[participant_id]]
  strength_data <- df %>% filter(measure == "Strength")
  nodes <- strength_data$node

  if (length(nodes) > 1) {
    node_pairs <- combn(nodes, 2)

    # Sort pairs to avoid duplicates
    sorted_pairs <- apply(node_pairs, 2, function(x) paste(sort(x), collapse = "__"))

    # ADD PARTICIPANT ID!!
    participant_pairs <- data.frame(
      Node_Pair = sorted_pairs,
      Participant_ID = gsub("_centr_means_imputed.csv", "", participant_id)
    )

    co_occurrence_list[[participant_id]] <- participant_pairs
  }
}

# frequency of each symptom pair in mean networks
co_occurrence_combined <- do.call(rbind, co_occurrence_list)

co_occurrence_counts <- co_occurrence_combined %>%
  group_by(Node_Pair) %>%
  summarize(Frequency = n(), Participants = paste(unique(Participant_ID), collapse = ", ")) %>%
  arrange(desc(Frequency))

colnames(co_occurrence_counts) <- c("Node_Pair", "Frequency", "Participants")

(co_occurrence_counts_means <- co_occurrence_counts[order(-co_occurrence_counts$Frequency), ])

(Mean_pairs <- ggplot(co_occurrence_counts_means, aes(x = reorder(Node_Pair, Frequency), y = Frequency)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Frequency of Unique Co-occurring Symptom Pairs - mean",
    x = "Symptom Pairs",
    y = "Frequency"
  ) +
  theme_minimal())

pdf("Idio_mean_symptom_pairs_frequency.pdf", width = 7, height = 35)
Mean_pairs
dev.off()
```

# Symptom pairs with one specified central means symptom 
```{r Mean node combination}
central_symptom <- "feelfat"

co_occurrence_counts_means$Node_Pair <- as.character(co_occurrence_counts_means$Node_Pair)

(central_pairs <- co_occurrence_counts_means %>%
  filter(grepl(central_symptom, Node_Pair))) # filter for pairs with specified symptom above

paired_symptoms <- do.call(rbind, strsplit(central_pairs$Node_Pair, "__")) # Split for itemized
(paired_symptoms <- unique(paired_symptoms[paired_symptoms != central_symptom])) # list of all it co-occurred with
```

# how many symptom ~pairs appeared in variability networks across participants?
```{r SD combination nodes}
co_occurrence_list <- list()

for (participant_id in names(data_lst_sds)) {
  df <- data_lst_sds[[participant_id]]
  strength_data <- df %>% filter(measure == "Strength")
  nodes <- strength_data$node

  if (length(nodes) > 1) {
    node_pairs <- combn(nodes, 2)

    # Sort pairs to avoid duplicates
    sorted_pairs <- apply(node_pairs, 2, function(x) paste(sort(x), collapse = "__"))

    # ADD PARTICIPANT ID!!
    participant_pairs <- data.frame(
      Node_Pair = sorted_pairs,
      Participant_ID = gsub("_centr_sd_imputed.csv", "", participant_id)
    )

    co_occurrence_list[[participant_id]] <- participant_pairs
  }
}

# frequency of each symptom pair in fluctuating networks
co_occurrence_combined <- do.call(rbind, co_occurrence_list)

co_occurrence_counts <- co_occurrence_combined %>%
  group_by(Node_Pair) %>%
  summarize(Frequency = n(), Participants = paste(unique(Participant_ID), collapse = ", ")) %>%
  arrange(desc(Frequency))

colnames(co_occurrence_counts) <- c("Node_Pair", "Frequency", "Participants")

(co_occurrence_counts_SD <- co_occurrence_counts[order(-co_occurrence_counts$Frequency), ])

(SD_pairs <- ggplot(co_occurrence_counts_SD, aes(x = reorder(Node_Pair, Frequency), y = Frequency)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Frequency of Unique Co-occurring Symptom Pairs - SD",
    x = "Symptom Pairs",
    y = "Frequency"
  ) +
  theme_minimal())
```

# Symptom pairs with one specified central variable symptom 
```{r SD node combination}
central_symptom <- "feelfat"

co_occurrence_counts_SD$Node_Pair <- as.character(co_occurrence_counts_SD$Node_Pair)

(central_pairs <- co_occurrence_counts_SD %>%
  filter(grepl(central_symptom, Node_Pair))) # filter for pairs

paired_symptoms <- do.call(rbind, strsplit(central_pairs$Node_Pair, "__")) # Split for itemized
(paired_symptoms <- unique(paired_symptoms[paired_symptoms != central_symptom])) # list of all it co-occurred with
```
