---
title: "05c_pres_analysis"
author: "Sglatt"
date: "`r Sys.Date()`"
output: html_document
---

# Nomothetic & idiographic dimensionality; ergodicity
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
if (!require("dplyr")) {install.packages("dplyr"); require("dplyr")} 
if (!require("EGAnet")) {install.packages("EGAnet"); require("EGAnet")} 
if (!require("readr")) {install.packages("readr"); require("readr")} 
if (!require("psych")) {install.packages("psych"); require("psych")} 
if (!require("purrr")) {install.packages("purrr"); require("purrr")} 
if (!require("stringr")) {install.packages("stringr"); require("stringr")} 
```

# Pull imputed data from 31 participants with < 50% raw data missing and combine into a single dataset
```{r import data}
main_dir <- "Created_data" # Folder with imputed data for each person created from script 01
folders <- list.dirs(main_dir, recursive = FALSE)

# These participants had <50% raw data
exclude_folders <- c("PR104", "PR089", "PR086", "PR084", "PR082", "PR079", "PR074", "PR073")

folders_to_include <- folders[!basename(folders) %in% exclude_folders]

get_files <- function(folder) {
  pr_name <- basename(folder) 
  pattern <- paste0("^", pr_name, "_imputed_rawwithtime.*\\.csv$")  
  list.files(folder, pattern = pattern, full.names = TRUE)
}

files_to_read <- map(folders_to_include, get_files) %>% unlist()

# combine all participant data
all_data <- map_dfr(files_to_read, read_csv)
head(all_data) # look at it!
colnames(all_data)

# Merge in dx column from demographics spreadsheet
demos <- read.csv("Raw_data/Demographics.csv")

all_data <- all_data %>% 
  left_join(demos %>% select(ID, dx), by = "ID")

# look at dx breakdown
dx_totals <- all_data %>%
  group_by(ID) %>%
  slice(1) %>%  
  count(dx) %>%  
  ungroup() %>%
  count(dx)  

dx_totals

# Filter to only AN or AAN
all_data_an <- all_data %>%
  filter(dx %in% c("AAN", "AN"))
```

# remove variables for analysis
```{r data vars}
# Unique variable analysis
all_data_an_uva  <- UVA(
  data = all_data_an[, -c(1:9, 72)])

all_data_an_uva
all_data_an_uva$keep_remove

describe(all_data_an[, -c(1:9, 72)]) # aggregated across people

# Remove items
all_data_an_clean <- all_data_an %>%
  select(-fowg, -badperson, -bodydiss, -shame, -thought_death, -laxdiur, # Remove per UVA
         
         -badperson, -worthless, -thought_death, -vomit, -binge, -intrus_thought, -food_intrus, -sad,
         -selfharm, -drink_public, -heartrace, -rumination, -avoid_sit, -physsens_eat, -ridthoughts, 
         -chewspit, -memories, # remove because low endorsed.
         -intrus_thought, -scared, -impulse, -compulsion, -socialanx, -eat_public, -agitated, -sleep, -tired,
         -anxiety, -si, relax, -stress, -saa, -emo_overwhelm, -worryoverwhelm, -sens_body, -physsens)

colnames(all_data_an_clean)

# Remove other non-symptom extra variables
all_data_an_clean <- all_data_an_clean %>%
  select(-c(2:9))

describe(all_data_an_clean[, -1]) 
```

# dynamic EGA; 
# is similar to EGA but evaluates the degree to which nodes change together over time.
# communities of nodes represent dynamical factors containing items that change together as a function of time.
```{r}
parallel::detectCores()

# Individual structures with first-order derivatives
(dyn_ega_d1 <- dynEGA(
  data = all_data_an_clean %>% filter(!ID %in% c("PR020", "PR042")), # need to remove on account of non-moving time d's
  n.embed = 5, tau = 1,
  delta = 1, id = 1, group = "dx", 
  use.derivatives = 1, 
  level = c("population", "group", "individual"),
  model = "glasso", algorithm = "walktrap", 
  corr = "cor_auto",
  ncores = 4
))

dyn_ega_d1

# Derive first-order derivatives
str(dyn_ega_d1)
str(dyn_ega_d1$Derivatives)
# dyn_ega$Derivatives$Estimates$PR007
# Derivatives_PR007 <- as.data.frame(dyn_ega$Derivatives$Estimates$PR007)
# View(Derivatives_PR007)

dyn_ega_d1$Derivatives$EstimatesDF
Derivatives_data <- as.data.frame(dyn_ega_d1$Derivatives$EstimatesDF)

# plots
plot(dyn_ega_d1$dynEGA$population)
plot(dyn_ega_d1$dynEGA$group)
plot(dyn_ega_d1$dynEGA$individual)
plot(dyn_ega_d1$dynEGA$individual, id = "PR003")

# save images
pdf("05c_Output/dynamic_ega_pop.pdf", width = 7, height = 7)
plot(dyn_ega_d1$dynEGA$population)
dev.off()

pdf("05c_Output/dynamic_ega_group.pdf", width = 14, height = 7)
plot(dyn_ega_d1$dynEGA$group)
dev.off()

pdf("05c_Output/dynamic_ega_individual.pdf", width = 14, height = 14)
plot(dyn_ega_d1$dynEGA$individual)
dev.off()
```

# empirical ergodicity information index for the full sample
```{r EII full}
# needs a slightly different dynEGA initial function that doesn't include group!

# need to remove group dx column from data
all_data_an_clean_2 <- all_data_an_clean %>%
  select(-27)

dyn_ega_d1_2 <- dynEGA.ind.pop(
  data = all_data_an_clean_2 %>% filter(!ID %in% c("PR020", "PR042")), 
  n.embed = 5, tau = 1,
  delta = 1, id = 1, 
  use.derivatives = 1, 
  model = "glasso", algorithm = "walktrap", 
  corr = "cor_auto",
  ncores = 4
)

dyn_ega_d1_2

plot(dyn_ega_d1_2$dynEGA$population) # note, this should 100% match the other dynEGA structure above
plot(dyn_ega_d1_2$dynEGA$individual) # ^ same goes for individuals

# Compute empirical ergodicity information index for the group
eii <- ergoInfo(dyn_ega_d1_2)
eii

set.seed(123456)
boot_eii <- boot.ergoInfo(
  dyn_ega_d1_2,
  eii,
  shuffles = 5000,
  iter = 100,
  ncores = 4,
  verbose = TRUE
)

boot_eii
plot(boot_eii)

# Golino, H., Nesselroade, J. R., & Christensen, A. P. (2022). Toward a psychology of individuals: The ergodicity information index and a bottom-up approach for finding generalizations. PsyArXiv.
```

# empirical ergodicity information index for the AN group
```{r EII an}
AN_data <- all_data_an_clean %>%
  filter(!ID %in% c("PR020", "PR042"), dx == "AN")

dyn_ega_an_only <- dynEGA.ind.pop(
  data = AN_data[, -27],
  n.embed = 5, tau = 1,
  delta = 1, id = 1, 
  use.derivatives = 1, 
  model = "glasso", algorithm = "walktrap", 
  corr = "cor_auto",
  ncores = 4
)

dyn_ega_an_only

plot(dyn_ega_an_only$dynEGA$population)
plot(dyn_ega_an_only$dynEGA$individual)

eii_an <- ergoInfo(dyn_ega_an_only)
eii_an

set.seed(123456)
boot_eii_an <- boot.ergoInfo(
  dyn_ega_an_only,
  eii_an,
  shuffles = 5000,
  iter = 100,
  ncores = 4,
  verbose = TRUE
)

boot_eii_an
plot(boot_eii_an)
```

# empirical ergodicity information index for the AAN group
```{r EEI aan}
AAN_data <- all_data_an_clean %>%
  filter(!ID %in% c("PR020", "PR042"), dx == "AAN")

dyn_ega_aan_only <- dynEGA.ind.pop(
  data = AAN_data[, -27], # remove dx
  n.embed = 5, tau = 1,
  delta = 1, id = 1, 
  use.derivatives = 1, 
  model = "glasso", algorithm = "walktrap", 
  corr = "cor_auto",
  ncores = 4
)

dyn_ega_aan_only

plot(dyn_ega_aan_only$dynEGA$population)
plot(dyn_ega_aan_only$dynEGA$individual)

# Compute empirical ergodicity information index for the group
eii_aan <- ergoInfo(dyn_ega_aan_only)
eii_aan

set.seed(123456)
boot_eii_aan <- boot.ergoInfo(
  dyn_ega_aan_only,
  eii_aan,
  shuffles = 5000,
  iter = 100,
  ncores = 4,
  verbose = TRUE
)

boot_eii_aan
plot(boot_eii_aan)
```

